\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Rohan Bali} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(123) 456-7890 $\vert$ Dartmouth, MA} 
\address{\href{mailto:rbali@umassd.edu}{rbali@umassd.edu} $\vert$ \href{https://www.linkedin.com/in/rohan-bali-301345293/}{LinkedIn} $\vert$ \href{https://github.com/rohanbalixz}{GitHub}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf M.S., Data Science, University of Massachusetts, Dartmouth} \hfill \textbf{Expected 2026}\\
Relevant Coursework: Advanced Machine Learning, Data Mining and Knowledge Discovery, Database Design, Small World Networks and Statistical Mathematics.

{\bf B.Tech., Computer and Communication Engineering, Manipal University, Jaipur} \hfill \textbf{2017 - 2021}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{TOOLS and SKILLS}
\begin{itemize}
    \itemsep -3pt{}
    \item Python, R, SQL, SciPy, Statsmodels, Scikit-learn, TensorFlow, Keras, PyTorch, Matplotlib, Seaborn, Plotly, ggplot2, Tableau, Power BI, Pandas, NumPy, dplyr (R), Hadoop, Spark, HDFS, Hive, Pig, Amazon S3, Google BigQuery, Azure Databricks, NLTK, SpaCy, Hugging Face Transformers, GitHub
    \item Probability and Statistics, Linear Algebra, Calculus, Optimization, Coding Proficiency, Algorithmic Thinking, Supervised and Learning, Model Evaluation and Validation, Data Cleaning, Data Transformation, Visual Storytelling, Communication, Report Writing, Analytical and Critical Thinking, Curiosity and Research skills, Data Ethics and Privacy 
\end{itemize}
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{CAPGEMINI $\vert$ Software Engineer} \hfill Dec 2021 - Jul 2024, Mumbai, India\\
\vspace{-\baselineskip} 
 \begin{itemize}
    \itemsep -3pt {} 
     \item Proactively monitor cloud infrastructure components, including compute, storage, networking, and security, to ensure high availability, scalability, and performance for clients such as IKEA, SEQUANA and ALE.
     \item Manage job scheduling, execution, and completion in cloud environments, leveraging automation tools and frameworks to streamline processes and minimize manual intervention.
    \item Strong understanding of cloud computing principles and technologies, with hands-on experience in managing cloud infrastructure services (e.g., AWS, Azure, GCP).
    \item Proficiency in scripting and automation using tools like Python, PowerShell, or Bash to automate repetitive tasks and improve operational efficiency.
 \end{itemize}
 
\textbf{UPCRED.AI $\vert$ Machine Learning Trainee} \hfill Aug 2021 - Dec 2021, Bengaluru, India\\
\vspace{-\baselineskip} 
 \begin{itemize}
    \itemsep -3pt {} 
     \item Spearheaded web scraping initiatives using Beautiful Soup to extract pertinent data from various online sources, facilitating data collection and preprocessing for machine learning projects.
     \item Employed MongoDB as the primary database solution to store scraped data efficiently, ensuring seamless accessibility and scalability for downstream analysis and model development.
    \item Collaborated with the client, Meesho, to understand data requirements and develop tailored web scraping strategies to gather relevant data from diverse online platforms.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Road Safety Analysis Using Machine Learning.} {The Road Safety Analysis project for Indian highways, diverse machine learning models like linear regression, KNN, random forest, SVM, etc., were employed. These models analyzed various factors to determine the safest highways in India. Through predictive analytics, they assessed variables such as traffic volume, road conditions, accident history, and weather patterns to identify highways with the lowest risk of accidents, aiding in strategic road planning and safety enhancement measures.}
\item \textbf{Movie Recommendation System.} {Harnessing data from 5000 movies on TMDB, I implemented a Bag of Words model for natural language processing. Utilizing vectorization techniques like TF-IDF, the system generates five tailored movie recommendations based on your selection. This method enhances accuracy and personalization.}
\end{rSection} 




\end{document}
